---
title: "Fiche visite"
params:
  siret: '34322975300037'
output:
  html_notebook: default
---


```{r setup, echo=FALSE, message=FALSE}
library("opensignauxfaibles")
library("lubridate")
database_signauxfaibles <- database_connect()
sirene <- get_sirene(db = database_signauxfaibles, .siret = params$siret)
```

## Informations principales

- Raison sociale : `r get_raisonsociale(db = database_signauxfaibles, .siret = params$siret)`
- SIRET : `r params$siret`
- SIREN : `r sirene$siren`
- Numero URSSAF : `r get_accountnumber(db = database_signauxfaibles, .siret = params$siret)`
- Date de création : `r format(ymd(paste0(sirene$date_creation_etablissement, "-01")), "%m-%Y")` (source SIRENE)
- Secteur d'activité : `r sirene$libelle_naf_niveau1`

## Effectif

```{r}
get_effectif(db = database_signauxfaibles, .siret = params$siret)
```

```{r plot-effectif}
plot_effectif(db = database_signauxfaibles, .siret = params$siret)
```

## Plan CCSF

```{r plan-ccsf}
is_ccsf(db = database_signauxfaibles, siret = params$siret)
```

## Cotisations

```{r}
get_meancotisation(db = database_signauxfaibles, siret = params$siret)
```

```{r}
plot_meancotisation(db = database_signauxfaibles, siret = params$siret)
```


